\cvsection{Conferences Attended}
\begin{conferences}
  \conference
    {}
    {\href{https://www.indiana.edu/~gstc/}{Graduate Student Topology \& Geometry Conference}}
    {Indiana University Bloomington}
    {Apr. 2016}
  \conference
    {}
    {\href{http://www.math.ku.dk/english/research/conferences/2017/stratifications-and-duality/}{Masterclass on Stratifications and duality in modular representation theory}}
    {University of Copenhagen}
    {Mar. 2017}
  \conference
    {}
    {\href{http://www-cgi.uni-regensburg.de/Fakultaeten/MAT/sfb-higher-invariants/index.php/SpringSchool2017}{Conference on invertible objects and duality in derived algebraic geometry and homotopy theory}}
    {University of Regensburg}
    {Apr. 2017}
  \conference
    {}
    {\href{http://hessbellwald-lab.epfl.ch/talbot17}{European Talbot Workshop - Dualities in Algebra, Geometry, and Topology}}
    {Lower Saxony, Germany}
    {Jun. 2017}
  \conference
    {}
    {\href{http://www.math.illinois.edu/homotopy2017/}{Homotopy Theory: tools and applications}}
    {UIUC}
    {Jul. 2017}
  \conference
    {}
    {\href{https://sites.google.com/site/eclipseconference/}{Homotopy Theory in the Ecliptic}}
    {Reed College}
    {Aug. 2017}
  \conference
    {}
    {\href{http://www.math.northwestern.edu/~pvankoug/MTS2018/index.html}{Midwest Topology Seminar}}
    {Northwestern University}
    {Mar. 2018}    
  \conference
    {}
    {\href{http://www.ams.org/meetings/sectional/2250_program_ss29.html}{AMS Spring Central Sectional Meeting, Special Session on Homotopy Theory}}
    {Ohio State University}
    {Mar. 2018}   
  \conference
    {}
    {\href{https://sites.google.com/view/chtjourney}{Chromatic Homotopy Theory : Journey to the Frontier}}
    {CU Boulder}
    {May 2018}
  \conference
    {}
    {\href{https://www.math-berlin.de/academics/summer-schools/2018}{Homotopy Theory Summer - Berlin 2018}}
    {Berlin Math School}
    {Jun. 2018}
  \conference
    {}
    {\href{https://www.newton.ac.uk/event/hhhw01}{Higher Structures in Homotopy Theory}}
    {Isaac Newton Institute}
    {Jul. 2018}
  \conference
    {}
    {\href{http://www.math.ku.dk/english/research/conferences/2018/ytm2018/}{Young Topologist's Meeting 2018}}
    {University of Copenhagen}
    {Jul. 2018}
  \conference
    {}
    {\textbf{\href{https://web.ma.utexas.edu/users/richard.wong/slides/YTM_Picard_Group_Talk.pdf}{Speaker}}, \href{https://faculty.math.illinois.edu/~hquan4/GSTGC2019/index.html}{Graduate Student Topology \& Geometry Conference}}
    {UIUC}
    {Mar. 2019}
  \conference
    {}
    {\textbf{\href{https://web.ma.utexas.edu/users/richard.wong/slides/YTM_Picard_Group_Talk.pdf}{Speaker}}, \href{https://ytm2019.epfl.ch/}{Young Topologist's Meeting 2019}}
    {EPFL}
    {Jul. 2019}
  \conference
    {}
    {\href{https://sites.google.com/view/etda2019/}{Equivariant Topology \& Derived Algebra: A Jolly Pleasant Conference for Greenlees}}
    {NTNU}
    {Aug. 2019}
  \conference
    {}
    {\textbf{\href{https://web.ma.utexas.edu/users/richard.wong/slides/NishidaNilpotenceTalk.pdf}{Speaker}}, \href{https://s.wayne.edu/isaksen/echt/kan-seminar/}{eCHT Kan Seminar}}
    {Online}
    {Sep. 2019}
  \conference
    {}
    {\href{https://nilesjohnson.net/mayday2019/}{Mayday 2019}}
    {University of Chicago}
    {Oct. 2019}
  \conference
    {}
    {\textbf{\href{https://web.ma.utexas.edu/users/richard.wong/slides/Picard_Groups_of_Stable_Module_Categories.pdf}{Speaker}}, \href{https://sites.google.com/view/sarahpetersen/groot-summer-seminar}{GROOT Summer Seminar}}
    {Online}
    {July 2020}
 \conference
    {}
    {\textbf{Speaker}, UChicago-Northwestern Topology Seminar}
    {Northwestern University}
    {Oct. 2020}
 \conference
    {}
    {\textbf{Speaker}, \href{https://s.wayne.edu/echt/electronic-algebraic-topology-employment-network/}{electronic Algebraic Topology Employment Network}}
    {Online}
    {Oct. 2020}
 \conference
    {}
    {\textbf{Speaker}, UIUC Topology Seminar}
    {UIUC}
    {Oct. 2020}
 \conference
    {}
    {\textbf{Speaker}, OSU Student Homotopy Theory Seminar}
    {OSU}
    {Oct. 2020}
  \conference
    {}
    {\textbf{Speaker}, \href{https://s.wayne.edu/echt/echt-reading-seminars/echt-kervaire-invariant-one-reading-seminar/}{eCHT Kervaire Invariant One Reading Seminar}}
    {Online}
    {Nov. 2020}
\end{conferences}
